WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-03-23 article/Article.tex
more references
darcs-hash:20060323092432-2fc9d-2a5f80d69c44f15920798a71eac8fe776cadc35d.gz

  \item \verb$itk.show()$, \verb$itk.show2D()$ and \verb$itk.show3D()$ are used to
display images. \verb$itk.show2D()$ requires to have \verb$imview$ installed.
\verb$itk.show3D()$ requires to have ItkVtk, PyQt, and iPython installed, and to use
iPython with the \verb$-qthread$ option.

>>>>

  \item \verb$itk.show()$, \verb$itk.show2D()$ and \verb$itk.show3D()$ are used to
display images. \verb$itk.show2D()$ requires to have imview \cite{ImviewWebSite} installed.
\verb$itk.show3D()$ requires to have ItkVtkGlue\footnote{ItkVtkGlue can be found in
the {\em ExternalProject} directory of WrapITK}, PyQt \cite{PyQtWebSite}, and iPython
\cite{IPythonWebSite} installed, and to use iPython with the \verb$-qthread$ option.
